The Astropy Project

### 2017-11-12 main.tex
grammar

\begin{description}
    \item[Barycentric and Heliocentric corrections] Detailed eclipse or transit
        timing requires accounting for light travel time differences from the
        source to the observatory because of the Earth's motion.
        It is therefore common to instead convert times to the Solar System
        barycenter or heliocenter where the relative timing of photons is
        standardized.
        With the location of a source on the sky (i.e. a \texttt{SkyCoord}
        object), the location of an observatory on Earth (i.e. an
        \texttt{EarthLocation} object), and time values as \texttt{Time}
        objects, the time corrections to shift to the solar system barycenter or
        heliocenter can now be computed with \package{astropy.time} using the
        \texttt{light\_travel\_time} method of a \texttt{Time} object.
    \item[\texttt{Time} objects in \texttt{Table}'s] \texttt{Time} objects can
        now be added as columns in \package{astropy.table} \texttt{Table}
        objects.
        This is described in more detail in \sectionname~\ref{sec:table} with
        the concept of a ``mixin'' column type.
\end{description}

>>>>

\begin{description}
    \item[Barycentric and Heliocentric corrections] Detailed eclipse or transit
        timing requires accounting for light travel time differences from the
        source to the observatory because of the Earth's motion.
        It is therefore common to instead convert times to the Solar System
        barycenter or heliocenter where the relative timing of photons is
        standardized.
        With the location of a source on the sky (i.e. a \texttt{SkyCoord}
        object), the location of an observatory on Earth (i.e. an
        \texttt{EarthLocation} object), and time values as \texttt{Time}
        objects, the time corrections to shift to the solar system barycenter or
        heliocenter can now be computed with \package{astropy.time} using the
        \texttt{light\_travel\_time} method of a \texttt{Time} object.
    \item[\texttt{Time} objects as \texttt{Table} columns] \texttt{Time} objects
        can now be added as columns in \package{astropy.table} \texttt{Table}
        objects. This is described in more detail in
        \sectionname~\ref{sec:table} with the concept of a ``mixin'' column
        type.
\end{description}
